Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Fixing my makefile

\section{What is uncertainty (I)}
\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown. Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence} [1]. \\

@@

@@

\subsection{Domains \& Applications (I)}

\section{Historic Overview}

@@

\subsubsection{1990 - 2000 (I)}

@@

\subsection{Compare FF-Replan with RFF (I\&A)}

@@

\subsection{Alternatives FF-Replan ()}

\subsection{What after? Any new methods (A)}

>>>>

\section{What is uncertainty (I)}

\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown. Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence} [1]. \\

@@

In the rest of this topic discuss the different domains and applications.

@@

\section{Historic Overview}
A swift introduction to the evolution of planning algorithms. For every problem state the:
\begin{itemize}
	\item The problem definition
	\item The motivation for the solution
	\item The strengths
	\item The weaknesses
\end{itemize}

@@

\subsection{1990 - 2000 (I)}
Choose 3 of these depending on what comes out in the different era's:

Model Checking, search techniques, least commitment - probabilistic planner (BURIDAN), DMCPs, dynamic programming, graphplan

Still need to check papers, but already have a bunch.

@@

\section{Compare FF-Replan with RFF (I\&A)}

@@

\section{What after? Any new methods (A)}
